### 2024-06-05 preregistration/README.qmd
README files

---
title: ""
format: 
  html:
    css: D:/repositories/liss_ef_2024/assets/style.css
    template: ../assets/template.html
bibliography: ../manuscript/references.bib
csl: ../manuscript/apa.csl
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---

@@

pagedown::chrome_print(input = "preregistration/README.html", output = "preregistration/preregistration.pdf")
```

[click here to download a pdf version](https://github.com/Schecher1/Minecraft-Server-Creator/blob/master/README.md)

@@

The independent measures used in this study are drawn from studies that were previously conducted in the Longitudinal Internet studies for the Social Sciences (LISS) panel.
These data are openly available after signing an agreement with LISS.
The dependent measures will be part of a new data collection in the LISS panel which is scheduled between May 2024 and July 2024.

>>>>

---
title: ""
format: 
  html:
    css: D:/repositories/liss_ef_2024/assets/style.css
    template: ../assets/template.html
    keep_md: true
bibliography: ../manuscript/references.bib
csl: ../manuscript/apa.csl
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---

@@

[click here to download a pdf version](https://github.com/StefanVermeent/liss_ef_2024/blob/main/preregistration/preregistration.pdf)

@@

The independent measures used in this study are drawn from studies that were previously conducted in the Longitudinal Internet studies for the Social Sciences (LISS) panel.
These data are openly available after signing an agreement with LISS.
The dependent measures will be part of a new data collection in the LISS panel which is scheduled in May and June 2024.
